\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{Organic reactivity}
The questions are primarily sourced from tutorial papers from the Technical University of Munich, Germany, exploring reactions and mechanisms in organic chemistry.

>>>>

\subparagraph{Organic reactivity}
The questions are primarily sourced from tutorial papers from the Technical University of Munich (Germany) exploring reactions and mechanisms in organic chemistry.
